### 2021-07-12 src/paper/data/share_known_cases.tex

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see
Section~\ref{sub:testing} for a detailed description for how we model both rapid and PCR
tests). For our model it is important to have an estimate for the share of cases that is
detected in the absence of rapid tests ($\psi_t$). For this we rely on the
\cite[Dunkelzifferradar Project][]{Dunkelzifferradar2020} which uses estimates of the case
fatality rate to estimate the number of total cases given the number of CoViD-19 deaths
which are assumed to be perfectly observable. For 2020, we follow the reported share of
detected cases quite closely \textcolor{red}{only interpolating the phase of November
2020 where the testing policy was changed to give more priority to vulnerable groups
\citep{RKI2020a}. This lead to more tests being done among older age groups which are
also at the highest risk of dying from CoViD-19. We suspect that this led the estimated
share of detected cases to increase without a corresponding increase in the share of
detected cases in the overall population as PCR tests, a rare resource at the time, were
only moved to groups with a high case fatality ratio.}

>>>>

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see
Section~\ref{sub:testing} for a detailed description for how we model both rapid and PCR
tests). For our model it is important to have an estimate for the share of cases that is
detected in the absence of rapid tests ($\psi_t$). For this we rely on the
\cite[Dunkelzifferradar Project][]{Dunkelzifferradar2020} which uses estimates of the
case fatality rate to estimate the number of total cases given the number of CoViD-19
deaths which are assumed to be perfectly observable. For 2020, we follow the reported
share of detected cases quite closely. One exception is the phase of November 2020 where
we interpolate to maintain monotonicity during the fall as there was no reason why the
share of detected cases should have risen in that time\footnote{The testing policy
changed in November \citep{RKI2020a}. However, this only moved the rare PCR tests more
towards vulnerable groups.}

### 2021-07-12 src/paper/model/number_of_contacts.tex

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only
those 50 people had contact with an infectious person and the disease has an infection
probability of 1 per contact or whether everyone met an infectious person but the
disease has an infection probability of only 5 percent per contact. SEIR models do not
distinguish contact frequency from the infectiousness of each contact and
combine the two in one parameter that is not invariant to social distancing policies.

To model social distancing policies, we need to disentangle the effects of the number of
contacts of each individual and the effect of policy-invariant infection probabilities
specific to each contact type. Since not all contacts are equally infectious, we
distinguish different contact types.

>>>>

Consider a hypothetical population of 1,000 individuals in which 50 were infected with a
novel infectious disease. From this alone, it is impossible to say whether only those 50
people had contact with an infectious person and the disease has an infection probability
of one or whether everyone met one infectious person but the disease has an infection
probability of only 5 percent per contact. SEIR models do not distinguish between the
number of contacts and the infectiousness of each contact. Instead, they combine the two
into one parameter that is not invariant to social distancing policies.

To model social distancing policies, we need to disentangle the effects of the number of
contacts of each individual and the effect of mostly policy-invariant infection
probabilities specific to each contact type. Since not all contacts are equally
infectious, we distinguish different contact types.
